Historical trends in the contribution of six major causes of death to the black-white

### 2017-05-19 Manuscript/Manuscript_COD_Trends.Rmd
further manu edits

Department of Epidemiology, Biostatistics and Occupational Health, McGill University, Montreal, Canada.

Address correspondence to: Corinne Riddell, PhD, Department of Epidemiology, Biostatistics & Occupational Health, McGill University, 1020 Pine Avenue West, Room 36B, Montreal, QC H3A 1A2, Canada. Email: <corinne.riddell@mail.mcgill.ca>

@@

@@

****

@@

>>>>

All authors: Department of Epidemiology, Biostatistics & Occupational Health, McGill University, 1020 Pine Avenue West, Room 36B, Montreal, QC H3A 1A2, Canada.

Address correspondence to: Corinne Riddell, PhD, Department of Epidemiology, Biostatistics & Occupational Health, McGill University, 1020 Pine Avenue West, Room 36B, Montreal, QC H3A 1A2, Canada. Email: <corinne.riddell@mail.mcgill.ca>. Phone: +1-438-863-0402

@@

###Significance statement: Add 120 word max statement.

@@

@@

**Stacked charts - not to be included in the submission**
